Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and Procedures

### 2012-05-13 rules/rules12.tex
Updating rules to reflect our use of SMT-Exec instead of StarExec

\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and 
Procedures \\
\small{Draft for comment \\
(comments due to organizers by 31 January 2012)}
}

@@

\noindent This is a preliminary version of the 2012 SMT-COMP rules, issued for comment
by potential participants. Comments should be emailed to the smtcomp mailing
list or, if necessary, directly to the organizers. To receive full consideration,
comments must be received by 31 January 2012.

@@

\item In the main and parallel competition, we are concentrating on just a few of the benchmark divisions this year.
  Some divisions, such as QF\_UF, are subsumed into more expressive
  logics; others have received only light interest in past competitions. Our goal is to
  focus the competition on divisions of particular interest to
  applications. Solvers requesting to be run against other benchmark divisions are
  welcome and will be run in exhibition mode:
  results will be displayed and publicly reported.

@@

\item The competition will be run with a new StarExec service, replacing
  the previous SMT-Exec service. At this writing, the new service is
  still being completed and tested; it will be announced later. (The
  previous service will be maintained in reserve.)

@@

\header{Solver format.} %
An entrant to SMT-COMP is an SMT solver
submitted using the StarExec\footnote{StarExec is still under development as of 21 January 2012;
updates on its progress and use will be posted on www.smtcomp.org and through
the SMT-COMP mailing list. Statements in these rules may need correction once the UI for the service is completed.} service.  
StarExec enables members of the
SMT research community to run solvers on jobs consisting of benchmarks
from the SMT-LIB benchmark library.  Jobs are run on a computer
cluster purchased with funds from a National Science Foundation
Computing Research Infrastructure grant.  StarExec is provided free of
charge, but it does require a minimal registration, which verifies an
email address and prevents misuse of the service.  Registered users
may then upload their own solvers to run, or may run public solvers
already uploaded to StarExec.  StarExec provides a variety of tabular
and graphical displays of results of solver executions, for
comparison. For the main (sequential-solver)
% rb 23/3: I guess also application track runs on 
% the same clusters as sequential
and application tracks 
of SMT-COMP 2012, StarExec will be configured so that jobs are run on a 64-bit,
uniprocessor Linux kernel.  For the parallel-solver track, StarExec
will be configured so that jobs are run on a 64-bit, multiprocessor
Linux kernel.

For participation in SMT-COMP, a solver must be
uploaded as a ``competition'' solver via the StarExec upload
mechanism, or, alternatively, a previously-uploaded solver may be
marked as a ``competition'' solver.  In either case, \emph{uploads
must be marked for competition before the deadline;} uploading a solver
to StarExec is not sufficient for competition entry if it is not marked
as being a competition entrant.  The md5 checksums of competition
submissions will be public immediately after the deadline for competition
entry has passed to ensure transparency, and the submissions themselves
will be made public after the competition.  Source code need not be
provided.  However, in order to encourage sharing of source code, extra
recognition will be given to solvers providing source code distributions
including recognition for the top such solver in each division.  Instructions
for uploading solvers and machine specifications will be posted as soon
as they are available.

\header{System description.} %
As part of their submission via StarExec,
SMT-COMP entrants must also include a short (1--2 pages) description of
the system.  This should include a list of all authors of the system
and their present institutional affiliations.  The programming
language(s) and basic SMT solving approach employed should be
described (\eg, lazy integration of a Nelson-Oppen combination with
SAT, translation to SAT, etc.).  System descriptions are encouraged to
include a URL for a web site for the submitted tool, but this is
optional.  System descriptions must also include a 32-bit unsigned
integer.  These numbers, collected from all submissions, are used
to seed the pseudo-random benchmark selection algorithm, as well
as the benchmark scrambler.

The StarExec upload system will ask for the system description and
the random seed when a solver is marked for competition, so
their inclusion in the uploaded archive itself is optional.

@@

\paragraph{Main competition track.} %
SMT-COMP entries must be submitted via StarExec by 7pm, Eastern U.S.
time, June~15, 2012.  At that time the StarExec service will be
closed to the public to prepare for the competition, with the
exception that resubmissions of existing entries will be accepted
until 7pm, Eastern U.S. time, June~18, 2012.  We strongly encourage
participants to use this weekend grace period \emph{only} for the
purpose of fixing any bugs that may be discovered and not for adding
new features as there will be no opportunity to do extensive testing
using StarExec after the original deadline on June~15.

The versions that are present on StarExec at the conclusion of the
grace period will be the ones used for the competition, and versions
submitted after this time will not be used.  The organizers reserve
the right to start the competition itself at any time after the open
of the New York Stock Exchange on the morning of June~20.  See
Section~\ref{sec:timeline} below for a full timeline.

@@

\paragraph{Parallel solver track.} %
Solvers employing concurrency are invited to participate in a
demonstration that will be run before the regular competition.
Parallel solvers must be submitted by the same June~15th deadline,
with the same grace period for resubmission as in the regular
competition.  Submissions to both the parallel solver track
and the main competition are independent: participants must submit
explicitly to both events to participate in both, and they may submit
different (or differently configured) solvers to each.  Benchmarks may
or may not be scrambled for this division.  Entrants should still
include a system description, as for the regular competition.

@@

Solvers will be publicly evaluated in the following tracks, listed here and 
described in detail below. In exhibition divisions of these tracks, solvers are evaluated and results posted, but no awards are announced. The other divisions are competition divisions; if there are sufficient entrants, a winner will be announced.
\begin{itemize}
\item a main track: sequential execution evaluated separately on benchmarks from each of several different logics (some competitive and some exhibition divisions)
\item a parallel track: parallel execution evaluated on the same benchmarks and the same divisions as the main track (some competitive and some exhibition divisions)
\item application track: evaluation on command scripts (all divisions with sufficient benchmarks and entrants are competitive)
\item unsat-core track: a competition among solvers capable of computing unsat cores
\item proof-generation exhibition: an exhibition track for solvers capable of generating proofs
\end{itemize}

@@

Similarly, the competition will feature an exhibition track of proof-generating solvers. This is
simply an exhibition track because there is as yet no SMT-LIB standard way to express proofs. We hope
that encouraging the capability in solvers will also encourage a common proof format. The exhibition
will count the number of benchmarks for which a solver successfully generates a proof.
Solvers submitted against this track must be accompanied by a description of the format of the 
generated proofs. The organizers are considering how and whether to check the proofs (with automated tools);
comment from teams submitting proof-generating solvers is welcome. %%TODO

The organizers are still reviewing which logic divisions will be supported for the unsat-core and proof generating tracks; 
those divisions will be announced later.
Input from teams considering submitting unsat-core or proof generating solvers is welcome.
%% TODO

@@

\item\label{step:pool} \textbf{Division selection pools created.} %
  For non-\emph{check} benchmarks, selection pools are created.
  For benchmark families with $\leq200$ eligible,
  non-\emph{check} benchmarks, all are added to this pool;
  otherwise, 200 such benchmarks are added to the pool with the
  following distribution:
%
  \begin{itemize}
  \item 20 with solution \textbf{sat} and difficulty on $\left[0,1\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(1,2\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(2,3\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(3,4\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(4,5\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left[0,1\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(1,2\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(2,3\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(3,4\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(4,5\right]$
  \end{itemize}
%
  If 20 are not available in one of these subdivisions, all that are
  available are added, and remaining slots are reallocated to the
  others.  This process is iterated so that it is guaranteed that 200
  benchmarks from the benchmark family are in the selection pool, in
  equal numbers from each subdivision, so far as possible.
  (In cases where \eg\ there are only two available slots and
  they can be allocated to one of three subdivisions, they are allocated
  randomly but are guaranteed to be allocated to \emph{distinct}
  subdivisions.)

@@

\nobreak
\vbox{% no page break here, please!
\begin{description}
\item[March 15] First version of the benchmark library for the application track posted for comment.
  First version of the benchmark scrambler, benchmark selector and trace exector made available.
\item[April 15] Final version of the benchmark scrambler, benchmark selector and trace exector made available.
\item[April 15] No new benchmarks can be added after this date, but
  problems with existing benchmarks may be fixed.
\item[June 1] Benchmark libraries are frozen.
\item[June 15 (7pm EDT)] Solvers due via StarExec (for
  all tracks), including system
  descriptions and magic numbers for benchmark scrambling.
\item[June 18 (7pm EDT)] Final versions due, fixing any last-minute
 bugs (this marks the end of the grace period for
 submissions).
\item[June 20] Opening value of NYSE Composite Index used to complete random seed.
\item[June 25--29] Anticipated dates for SMT-COMP 2012.
\end{description}}

>>>>

\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and 
Procedures}

@@

\noindent Comments on this document should be emailed to the smtcomp mailing
list or, if necessary, directly to the organizers.

@@

\item In the main and parallel competition, we are concentrating on just a few of the benchmark divisions this year.
  Some divisions, such as QF\_LIA, are subsumed into more expressive
  logics (QF\_UFLIA for QF\_LIA); others have received only light interest in past competitions. Our goal is to
  focus the competition on divisions of particular interest to
  applications. Solvers requesting to be run against other benchmark divisions are
  welcome and will be run in exhibition mode:
  results will be displayed and publicly reported.

@@

\item The competition will be run with the SMT-Exec service used last year.
  The organizers had expected to use a new StarExec service, replacing
  the previous SMT-Exec service. However, at this writing the new service
  is not yet available.

@@

\header{Solver format.} %
An entrant to SMT-COMP is an SMT solver
submitted using the SMT-Exec\footnote{The organizers may switch to StarExec, 
though Star-Exec is still under development as of 12 May 2012.} service.  
The execution service enables members of the
SMT research community to run solvers on jobs consisting of benchmarks
from the SMT-LIB benchmark library.  Jobs are run on a shared computer
cluster.  The execution service is provided free of
charge, but it does require a minimal registration, which verifies an
email address and prevents misuse of the service.  Registered users
may then upload their own solvers to run, or may run public solvers
already uploaded to the service.  The service provides a variety of tabular
and graphical displays of results of solver executions, for
comparison. For the main (sequential-solver)
% rb 23/3: I guess also application track runs on 
% the same clusters as sequential
and application tracks 
of SMT-COMP 2012, the service will be configured so that jobs are run on a 64-bit,
uniprocessor Linux kernel.  For the parallel-solver track, StarExec
will be configured so that jobs are run on a 64-bit, multiprocessor
Linux kernel.

For participation in SMT-COMP, a solver must be
uploaded as a ``competition'' solver via the service's upload
mechanism, or, alternatively, a previously-uploaded solver may be
marked as a ``competition'' solver.  In either case, \emph{uploads
must be marked for competition before the deadline}; uploading a solver
to the service is not sufficient for competition entry if it is not marked
as being a competition entrant.  The md5 checksums of competition
submissions will be public immediately after the deadline for competition
entry has passed to ensure transparency, and the submissions themselves
will be made public after the competition.  Source code need not be
provided.  However, in order to encourage sharing of source code, extra
recognition will be given to solvers providing source code distributions
including recognition for the top such solver in each division.  Instructions
for uploading solvers and machine specifications will be posted as soon
as they are available.

\header{System description.} %
As part of their submission,
SMT-COMP entrants must also include a short (1--2 pages) description of
the system.  This should include a list of all authors of the system
and their present institutional affiliations.  The programming
language(s) and basic SMT solving approach employed should be
described (\eg, lazy integration of a Nelson-Oppen combination with
SAT, translation to SAT, etc.).  System descriptions are encouraged to
include a URL for a web site for the submitted tool, but this is
optional.  System descriptions must also include a 32-bit unsigned
integer.  These numbers, collected from all submissions, are used
to seed the pseudo-random benchmark selection algorithm, as well
as the benchmark scrambler.

The upload system will ask for the system description and
the random seed when a solver is marked for competition, so
their inclusion in the uploaded archive itself is optional.

@@

\paragraph{Main competition track.} %
SMT-COMP entries must be submitted via SMTExec by 7pm, Eastern U.S.
time, June~15, 2012.  At that time the service will be
closed to the public to prepare for the competition, with the
exception that resubmissions of existing entries will be accepted
until 7pm, Eastern U.S. time, June~18, 2012.  We strongly encourage
participants to use this weekend grace period \emph{only} for the
purpose of fixing any bugs that may be discovered and not for adding
new features as there will be no opportunity to do extensive testing
using StarExec after the original deadline on June~15.

The versions that are present on the execution service at the conclusion of the
grace period will be the ones used for the competition, and versions
submitted after this time will not be used.  The organizers reserve
the right to start the competition itself at any time after the open
of the New York Stock Exchange on the morning of June~20.  See
Section~\ref{sec:timeline} below for a full timeline.

@@

\paragraph{Parallel solver track.} %
Solvers employing concurrency are invited to participate in a
demonstration that will be run in conjunction with the regular competition.
Parallel solvers must be submitted by the same June~15th deadline,
with the same grace period for resubmission as in the regular
competition.  Submissions to both the parallel solver track
and the main competition are independent: participants must submit
explicitly to both events to participate in both, and they may submit
different (or differently configured) solvers to each.  Benchmarks may
or may not be scrambled for this division.  Entrants should still
include a system description, as for the regular competition.

@@

Solvers will be publicly evaluated in the following tracks, listed here and 
described in detail below. In exhibition divisions of these tracks, solvers are evaluated and results posted, but no awards are announced. The other divisions are competition divisions; if there are sufficient entrants, a winner will be announced.
\begin{itemize}
\item a main track: sequential execution evaluated separately on benchmarks from each of several different logics (some competitive and some exhibition divisions)
\item a parallel track: parallel execution evaluated on the same benchmarks and the same divisions as the main track (some competitive and some exhibition divisions)
\item application track: evaluation on command scripts (all divisions with sufficient benchmarks and entrants are competitive)
\item unsat-core track: a competition among solvers capable of computing unsat cores
\item proof-generation exhibition: an exhibition track for solvers capable of generating proofs (this track is tentative, given that the organizers must work with the SMT-Exec service)
\end{itemize}

@@

Similarly, the competition will feature an exhibition track of proof-generating solvers. This is
simply an exhibition track because there is as yet no SMT-LIB standard way to express proofs and no
means of checking the proofs. We hope
that encouraging the capability in solvers will also encourage a common proof format. The exhibition
will count the number of benchmarks for which a solver successfully generates a proof.
Solvers submitted against this track must be accompanied by a description of the format of the 
generated proofs.

The organizers are still reviewing which logic divisions will be supported for the unsat-core and proof generating tracks; 
those divisions will be announced later.
Input from teams considering submitting unsat-core or proof generating solvers is welcome. In addition, because
the competition has had to revert to the SMT-Exec, the organizers may simply make the proof genreation demonstration 
informational or omit it.
%% TODO

@@

\item\label{step:pool} \textbf{Division selection pools created.} %
  For non-\emph{check} benchmarks, selection pools are created.
  For benchmark families with $\leq200$ eligible,
  non-\emph{check} benchmarks, all are added to this pool;
  otherwise, 200 such benchmarks are added to the pool with the
  following distribution:
%
  \begin{itemize}
  \item 20 with solution \textbf{sat} and difficulty on $\left[0,1\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(1,2\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(2,3\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(3,4\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(4,5\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left[0,1\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(1,2\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(2,3\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(3,4\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(4,5\right]$
  \end{itemize}
%
  If 20 are not available in one of these subdivisions, all that are
  available are added, and remaining slots are reallocated to the
  others.  This process is iterated so that it is guaranteed that 200
  benchmarks from the benchmark family are in the selection pool, in
  equal numbers from each subdivision, so far as possible.
  (In cases where, \eg, there are only two available slots and
  they can be allocated to one of three subdivisions, they are allocated
  randomly but are guaranteed to be allocated to \emph{distinct}
  subdivisions.)

@@

\nobreak
\vbox{% no page break here, please!
\begin{description}
\item[March 15] First version of the benchmark library for the application track posted for comment.
  First version of the benchmark scrambler, benchmark selector and trace exector made available.
\item[April 15] Final version of the benchmark scrambler, benchmark selector and trace exector made available.
\item[April 15] No new benchmarks can be added after this date, but
  problems with existing benchmarks may be fixed.
\item[June 1] Benchmark libraries are frozen.
\item[June 15 (7pm EDT)] Solvers due via SMTExec (for
  all tracks), including system
  descriptions and magic numbers for benchmark scrambling.
\item[June 18 (7pm EDT)] Final versions due, fixing any last-minute
 bugs (this marks the end of the grace period for
 submissions).
\item[June 20] Opening value of NYSE Composite Index used to complete random seed.
\item[June 25--29] Anticipated dates for SMT-COMP 2012.
\end{description}}
